Vision and Cognitive Systems Final Project

### 2020-06-30 Paper_Presentation/paper/paper.tex
paper updates

\section{Painting Retrieval}
For the retrieval of the paintings situated in the database we use an approach based on feature detection algorithms.\\ 
After consulting a paper that performs a comparative analysis between the most well known algorithms ~\cite{b1} to get a general idea of the strengths and weaknesses of the different methods available to us, we carried out some experiments focusing on SIFT, AKAZE and ORB.\\
The results obtained made us opt for ORB, because overall it gave us more precise results than AKAZE and, unlike SIFT, it’s free of charge, therefore usable without fees in a possible commercial application.\\
To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module [link pickle documentation].\\
It implements binary protocols for serializing and de-serializing a Python object structure.\\
This data is loaded only once during the launch of the program.
The key points are computed from the bounding boxes detected by the previously described pipeline and afterward, to determine the best matches, the ratio test proposed by D. Lowe in the SIFT paper is performed[Reference to the sift paper].\\
This measure is obtained by comparing the distance of the closest neighbor to that of the second-closest neighbor.\\
This measure performs well because correct matches need to have the closest neighbor significantly closer than the closest incorrect match to achieve reliable matching.\\
For false matches, there will likely be a number of other false matches within similar distances due to the high dimensionality of the feature space.\\
In our implementation we reject all matches in which the distance ratio is greater than 0.75.\\
This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positive.
A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.\\
To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 ranked is calculated and, if the first one differs from it for more than significant value, it is considered as correct and shown on the interface.

@@

@@

\section{People Detection}
A neural network (YoloV3) is used for people detection.\\
Each video frame is passed through the network tho make inference, and find all bounding boxes containing one of the objects in our classes list.\\
The weights for the network are obtained from an already trained network on COCO[ reference to COCO paper], a famous dataset containing 80 different classes.\\
In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class.\\
A little problem has arisen due to the high number of paintings representing persons, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.

\section{People Localization}
People Localization

\section{Painting Replacement in the 3D Model}
Painting Replacement in the 3D Model

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

@@

\begin{thebibliography}{00}
\bibitem{b1} Tareen, Shaharyar Ahmed Khan, and Zahra Saleem. "A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET). IEEE, 2018.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

>>>>

\section{Painting Retrieval}
For the retrieval of the paintings situated in the database we use an approach based on feature detection algorithms.\\ 
After consulting a paper that performs a comparative analysis between the most well known algorithms ~\cite{b1} to get a general idea of the strengths and weaknesses of the different methods available to us, we carried out some experiments focusing on SIFT, AKAZE and ORB.\\
The results obtained made us opt for ORB, because overall it gave us more precise results than AKAZE and, unlike SIFT, it’s free of charge, therefore usable without fees in a possible commercial application.\\
To save time, the key points of the paintings in the database have been previously calculated and stored using the pickle module [link pickle documentation].\\
It implements binary protocols for serializing and de-serializing a Python object structure.\\
This data is loaded only once during the launch of the program.
The key points are computed from the bounding boxes detected by the previously described pipeline and afterward, to determine the best matches, the ratio test proposed by D. Lowe in the SIFT paper is performed[Reference to the sift paper].\\
This measure is obtained by comparing the distance of the closest neighbor to that of the second-closest neighbor.\\
This measure performs well because correct matches need to have the closest neighbor significantly closer than the closest incorrect match to achieve reliable matching.\\

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
\caption{Orb matches}
\label{fig}
\end{figure}

For false matches, there will likely be a number of other false matches within similar distances due to the high dimensionality of the feature space.\\
In our implementation we reject all matches in which the distance ratio is greater than 0.75.\\
This allows us to keep the number of correctly retrieved paintings still high but at the same time to decrease the number of false positive.
A ranking with the 5 best matches found is then created and saved to a CSV file to show the results.\\
To understand if the painting is actually recognized among those in the DB, the average of the key points matched among the best 5 ranked is calculated and, if the first one differs from it for more than significant value, it is considered as correct and shown on the interface.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../detection_and_rectification/top_association_vid05.png}}
\caption{Painting detection and rectification}
\label{fig}
\end{figure}

@@

\section{People Detection}
A neural network (YoloV3) is used for people detection.\\
At inference time each video frame is passed through the network that find all bounding boxes containing one of the objects in our classes list.\\
The weights for the network are obtained from an already trained network on COCO[ reference to COCO paper], a famous dataset containing 80 different classes.\\
In our case the only wanted class is the person one, for ease of use the network has not been modified, but from its output will be deleted all the classes with an id different from 0 that is the id of the person class.\\

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/paint_and_person.png}}
\caption{People detection}
\label{fig}
\end{figure}

A little problem has arisen due to the high number of paintings representing persons, in fact the network detect them also inside the paintings, to prevent these false positive we added a new control on the pixel position in order to cut out all the people detected inside a bounding box previously classified as a painting.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error.png}}
\caption{People detection error}
\label{fig}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error_fixed.png}}
\caption{People detection error fixed}
\label{fig}
\end{figure}

\section{People Localization}
Starting from a previously detected and retrieved painting from the database, we search the corresponding room in csv file, then a little red dot is printed on the museum image map. With this method we assume that all the painting detected and the persons are in the same room.
Moreover the localization will work only if the painting matched is considered safe that means the painting need to have a good level of matches, otherwise localization is not active.

\section{Painting Replacement in the 3D Model}
the pipeline followed to accomplish this task is similar to the one explained before with a little difference. we start directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found. At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database. Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.
what is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification. this function in fact takes as input two images and project the first one on the plane of the second. if the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.

\section{Metrics and Precision}
To calculate the precision of the presented method we took almost 10 random frame for 6 different videos and labeled all the paintings by hand using a tool for labeling (normally used for yolo labels). Then with a custom code we calculated precision recall… comparing hand made labels with automatically generated ones.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
\caption{labeling.}
\label{fig}
\end{figure}

\begin{table}[htbp]
\caption{Metrics Table}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

@@

\begin{thebibliography}{00}
\bibitem{b1} Tareen, Shaharyar Ahmed Khan, and Zahra Saleem. "A comparative analysis of sift, surf, kaze, akaze, orb, and brisk." 2018 International conference on computing, mathematics and engineering technologies (iCoMET). IEEE, 2018.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
